Compressive Channel Sensing of Multipath Millimeter Channel via a Beamspace Dantzig Selector and its Probabilitic Performance Bound

### 2019-03-14 ongoing/report/4_simulation.tex
Simulation: Rev block matrix notation

As of now, we have transformed the sparse-recovery problem of complex matrix \m {H} to complex vector \m {h}, and finally to real vector \m {\MC {R} (h)}.
But it is not the end.
In fact, Cand\`es and Tao's analysis in ``\m {\ell_1}-MAGIC'' transforms DS into a linear program (LP), but that does not directly applies
Actually they pointed out that complex DS may be cast into a second order cone program (SOCP), but (as they admit in the paper) they did not pursue the matter.
Since the proof is, for the present purpose, not entirely trivial, we include here for completeness of exposition.
Thus our proposed algorithm is not a corollary of the DS program outlines in ``\m {\ell_1}-MAGIC''.

\startsection [title={Transformation into Second Order Cone Problem}]

@@

\Result
{Definition}
{
For \m {x \in \MB {V} (M)}, we say \m {\MC {R} (x)} is the real representation of \m {x}, defined by
%
\Disp {
\NC \MC {R} (x) \in \NC \MB {V} (2M) \NR[+]
\NC \MC {R} (x) \DB {m} =
\NC \startcases
\MF {Re} (\MC {R} (x)\DB {m}), \quad \MC m =2m' \NR
\MF {Im} (\MC {R} (x)\DB {m}), \quad \MC m =2m'+1 \NR
\stopcases \NR[+]
\NC m' \NC =  1, \dots, M \NR
}
%
}

@@

\Result
{Definition}
{
For \m {A \in \MB {M}_{\MB {C}} (M_1, M_2)}, we say \m {\MC {R} (A)} is the real representation of \m {A}, defined by
%
\Disp {
\NC A \in \NC \MB {V}_{\MB {R}} (2M_1, 2M_2) \NR[+]
\NC A (m_1,m_2) =
\NC \startcases
\MF {Re} (A (m_1,m_2)), \quad \MC m_1 =2m_1'-1,\; m_2 =2m_2'-1  \NR
\MF {Im} (A (m_1,m_2)), \quad \MC m_1 =2m_1',\; m_2 =2m_2'-1  \NR
-\MF {Im} (A (m_1,m_2)), \quad \MC m_1 =2m_1'-1,\; m_2 =2m_2'  \NR
\MF {Re} (A (m_1,m_2)), \quad \MC m_1 =2m_1',\; m_2 =2m_2'  \NR
\stopcases \NR[+]
\NC m_1' \NC = 1, \dots, m_1 \NR[+]
\NC m_2' \NC = 1, \dots, m_2 \NR
}
%
}

@@

%
\Disp {
\NC \V {\T {y}}
\NC = \MC {R} (y)
\in \MB {V} (N_h) \NR[+]
\NC \V {\T {g}}
\NC = \MC {R} (g)
\in \MB {V} (N_h) \NR[+]
\NC \M {\T {P}}
\NC = \MC {R} (\M {P})
\in \MB {M}_{\MB {C}} (2 N_y^2, 2 N_h^2) \NR
}
%
such that
%
\Disp {
\NC \V {\T {y}} \NC = \M {\T {P}} \V {\T {g}} +\V {\T {z}}
}
%
where by construction
%
\Disp {
\NC \V {\T {z}}
\NC = \MC {R} (\V {z}) \in \MB {V} (N_y) \NR
}
%

@@

%
\Disp {
\NC \M {I}_{n_y}^{(y)} \in \NC \MB {M}_{\MB {R}} (2N_y^2, 2N_y^2) \NR[+]
\NC \M {I}_{n_y}^{(y)} (n_y')
\NC =
\startcases
1, \quad \MC n_y' =2n_y \NR[+]
1, \quad \MC n_y' =2n_y +1 \NR[+]
0, \quad \NC otherwise
\stopcases \NR[+]
\NC \M {I}_{n_h}^{(h)} \in \NC \MB {M}_{\MB {R}} (2N_h^2, 2N_h^2) \NR[+]
\NC \M {I}_{n_h}^{(h)} (n_h')
\NC =
\startcases
1, \quad \MC n_h' =2n_h \NR[+]
1, \quad \MC n_h' =2n_h +1 \NR[+]
0, \NC otherwise
\stopcases \NR[+]
\NC n_y \NC = 1, \dots, N_y \NR[+]
\NC n_h \NC = 1, \dots, N_h \NR
}
%

If we introduce vector \m {\V {m}} to denote the entrywise complex modulus, we see that Program () now take the form

\Result
{Program}
{
Given are \m {\T {\M {P}}, \T {\V {y}}, \gamma}.
Find \m {\T {\V {g}}} with
%
\Disp {
\NC \T {\V {g}}
\NC = \startcases
\NC \Min {\T {\V {g}}, \V {m}} \quad
\MC \IP { \V {1}, \V {m} } \NR
\NC \RM {subject} \; \RM {to} \quad
\MC \VNm { \M {I}_{n_h}^{(h)} \T {\V {g}} }_2
\leq \IP { \V {y}_{n_h}, \V {m} } \NR
\NC \MC \VNm { \M {I}_{n_y}^{(y)} \T {\M {P}}^\H \RB { \T {\M {P}} \T {\V {g}} -\T {\V {y}} } }_2
\leq \gamma \NR
\stopcases \NR
}
%
where \m {\V {1}} is the all-1 vector.
}

The program, we see, is an SOCP.

We further rewrite Program () into a stricter, extended block matrix form to make the point clearer.

\color[red]{(To be done)}

@@

To clarify notation and for complentess of exposition, we derive the dual problem here.
Start with the Lagrangian \m {\MC {L}}, where we note we have to introduce one auxiliary vector and one auxiliary scalar for each \m {\ell_2}-norm constraint.

%
\Disp {
\NC \NC \MC {L} (\V {m}, \T {\V {g}}, \V {\mu}^{(h)}, \V {\mu}^{(y)}, \lambda^{(h)}, \lambda^{(y)}) \NR[+]
\NC \NC = \IP {\V {1}, \V {m}}
+\sum_{n_h} \SB {\IP {\V {\mu}^{(h)}, \M {I}_{n_h}^{(h)} \T {\M {g}}} -\lambda^{(h)} \IP {\V {y}_{n_h}, \V {m}}} \NR[+]
\NC \quad \NC  +\sum_{n_y} \SB { \IP { \V {\mu}^{(h)}, \M {I}_{n_y}^{(y)} \T {\M {P}}^\H ( \T {\M {P}} \T {\V {g}} -\T {\V {y}} ) } -\lambda^{(h)} \gamma} \NR[+]
}
%

>>>>

As of now, we have transformed the sparse-recovery problem of complex matrix \m {H} to complex vector \m {h}, and finally to real vector \m {\Mc {R} \SB {h}}.
But it is not the end.
In fact, Cand\`es and Tao's analysis in ``\m {\ell_1}-MAGIC'' transforms DS into a linear program (LP), but that does not directly applies
Actually they pointed out that complex DS may be cast into a second order cone program (SOCP), but (as they admit in the paper) they did not pursue the matter.
Since the proof is, for the present purpose, not entirely trivial, we include here for completeness of exposition.
Thus our proposed algorithm is not a corollary of the DS program outlines in ``\m {\ell_1}-MAGIC''.

\startsection [title={Transformation of the Problem}]

\startsubsection [title={Representation by Real Matrices}]

@@

\Result
{Definition}
{
For \m {x \in \Mb {V} \SB {M}}, we say that \m {\Mc {R} \SB {x}} is the real representation of \m {x}, defined by
%
\Disp {
\NC \Mc {R} \SB {x} \in \NC \Mb {V} \SB {2M} \NR[+]
\NC \Mc {R} \SB {x} \DB {m} =
\NC \startcases
\NC \Mf {Re} \SB {\Mc {R} \SB {x} \DB {m'}}, \MC m =2m' \NR
\NC \Mf {Im} \SB {\Mc {R} \SB {x} \DB {m'}}, \MC m =2m'+1 \NR
\stopcases \NR[+]
\NC m' = \NC  1, \dots, M \NR
}
%
}

@@

\Result
{Definition}
{
For \m {A \in \Mb {M}_{\Mb {C}} \SB {M_1, M_2}}, we say that \m {\Mc {R} \SB {A}} is the real representation of \m {A}, defined by
%
\Disp {
\NC A \in \NC \Mb {V}_{\Mb {R}} \SB {2M_1, 2M_2} \NR[+]
\NC A \DB {m_1,m_2} =
\NC \startcases
\NC \Mf {Re} \SB {A \SB {m_1',m_2'}}, \MC (m_1, m_2) = (2m_1'-1, 2m_2'-1) \NR
\NC \Mf {Im} \SB {A \SB {m_1',m_2'}}, \MC (m_1, m_2) = (2m_1', 2m_2'-1) \NR
\NC -\Mf {Im} \SB {A \SB {m_1',m_2'}}, \MC (m_1, m_2) = (2m_1'-1, 2m_2') \NR
\NC \Mf {Re} \SB {A \SB {m_1',m_2'}}, \MC (m_1, m_2) = (2m_1', 2m_2') \NR
\stopcases \NR[+]
\NC m_1' = \NC 1, \dots, m_1 \NR[+]
\NC m_2' = \NC 1, \dots, m_2 \NR
}
%
}

@@

%
\Disp {
\NC \V {\T {y}}
= \NC \Mc {R} \SB {y}
\in \Mb {V} \SB {2N_y} \NR[+]
\NC \V {\T {g}}
= \NC \Mc {R} \SB {g}
\in \Mb {V} \SB {2N_h} \NR[+]
\NC \M {\T {P}}
= \NC \Mc {R} \SB {\M {P}}
\in \Mb {M}_{\Mb {C}} \SB {2N_y, 2N_h} \NR[+]
\NC \V {\T {z}}
= \NC \Mc {R} \SB {\V {z}} \in \Mb {V} \SB {2N_y} \NR[+]
}
%
such that, by construction,
%
\Disp {
\NC \V {\T {y}} = \NC \M {\T {P}} \V {\T {g}} +\V {\T {z}}
}
%

@@

%
\Disp {
\NC {\T {\M {u}}}_{n_y}^{(y)} \in \NC \Mb {M}_{\Mb {R}} \SB {2N_y, 2N_y} \NR
\NC {\T {\M {u}}}_{n_y}^{(y)} \DB {m_y}
= \NC
\startcases
1, \quad \MC m_y =2n_y \NR
1, \quad \MC m_y =2n_y +1 \NR
0, \quad \NC {\rm otherwise}
\stopcases \NR[+]
\NC {\T {\M {U}}}_{n_h}^{(h)} \in \NC \Mb {M}_{\Mb {R}} \SB {2N_h, 2N_h} \NR
\NC {\T {\M {U}}}_{n_h}^{(h)} \DB {m_h, m_h'}
= \NC
\startcases
1, \quad \MC m_h =2n_h,\; m_h' =2n_h \NR
1, \quad \MC m_h =2n_h +1,\; m_h' =2n_h \NR
1, \quad \MC m_h =2n_h,\; m_h' =2n_h +1\NR
1, \quad \MC m_h =2n_h +1,\; m_h' =2n_h +1 \NR
0, \quad \NC {\rm otherwise}
\stopcases \NR[+]
\NC n_y, m_y = \NC 1, \dots, N_y \NR
\NC n_h, m_h, m_h' = \NC 1, \dots, N_h \NR
}
%

If we introduce vector \m {\V {m} \in \Mb {M}_{\Mb {V}} \SB {N_y}} to denote the entrywise complex modulus, we see that the convex optimization now take the form
\Disp {
\NC \T {\V {g}}
= \NC \startcases
\NC \Min {\T {\V {g}}, \V {m}} \quad
\MC \IP { \V {1}, \V {m} } \NR
\NC \Mr {subject} \; \Mr {to} \quad
\MC \VNm { \M {U}_{n_h}^{(h)} \T {\V {g}} }_2
\leq \IP { \V {u}_{n_h}, \V {m} } \NR
\NC \MC \VNm { \M {U}_{n_y}^{(y)} \T {\M {P}}^\Adj \RB { \T {\M {P}} \T {\V {g}} -\T {\V {y}} } }_2
\leq \gamma \NR
\stopcases \NR
}
where \m {\V {1} \in \Mb {M}_{\Mb {V}} \SB {N_y}} is the all-1 vector.

\stopsubsection

\startsubsection [title={Second Order Cone Problem}]

We shall see furthermore that the program can be cast into an SOCP.
To make the point clearer, we rewrite Program () into a stricter, extended block matrix form
\Result
{Algorithm}
{
\startitemize[n]
\item Input \m{\M {P} \in \Mb {M}_{\Mb {C}} \SB {N_y, N_h}}, \m{\V {y} \in \Mb {V}_{\Mb {C}} \SB {N_h}}, \m{\gamma \geq 0}.
\item Input \m{\hat {\M {P}} \in \Mb {M}_{\Mb {C}} \SB {N_y, N_h}}, \m{\hat {\V {y}} \in \Mb {V}_{\Mb {C}} \SB {N_h}}.
\item Calculate
\item Output \m {\hat {\M {H}}}.
\stopitemize
}

@@

To clarify notation and for complentess of exposition, we derive the dual problem here.
Start with the Lagrangian \m {\Mc {L}}, where we note we have to introduce one auxiliary vector and one auxiliary scalar for each \m {\ell_2}-norm constraint.

%
\Disp {
\NC \NC \Mc {L} \SB {\V {m}, \T {\V {g}}, \V {\mu}^{(h)}, \V {\mu}^{(y)}, \lambda^{(h)}, \lambda^{(y)}} \NR[+]
\NC = \NC \IP {\V {1}, \V {m}}
+\sum_{n_h} \SB {\IP {\V {\mu}^{(h)}, \M {I}_{n_h}^{(h)} \T {\M {g}}} -\lambda^{(h)} \IP {\V {y}_{n_h}, \V {m}}} \NR[+]
\NC \quad \NC  +\sum_{n_y} \SB { \IP { \V {\mu}^{(h)}, \M {I}_{n_y}^{(y)} \T {\M {P}}^\Adj \RB { \T {\M {P}} \T {\V {g}} -\T {\V {y}} } } -\lambda^{(h)} \gamma} \NR[+]
}
%
